Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-07-23 exp1/iswc2013.tex
Machine details in footnote
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@615 43ef1190-90fd-4dd7-a769-d0121f02b80e

We have chosen 8 factors each having 2 levels, ``TripleC'' the number
of triples in the data-set, 1 or 2 MTriples, ``Machine'', which is the
software and hardware platform, where one machine runs GNU/Linux
Debian Squeeze, has 16 GB RAM, an Intel Core2 Duo E8500 CPU and two
Parallel-ATA disks in a RAID-1 configuration. The other machine runs
Debian Wheezy, has 8 GB RAM, an Intel Core i7-3520M CPU and a single
SSD on SATA-III.

>>>>

We have chosen 8 factors each having 2 levels, ``TripleC'' the number
of triples in the data-set, 1 or 2 MTriples, ``Machine'', which is the
software and hardware platform, one larger with slower
disks\footnote{Running GNU/Linux Debian Squeeze, has 16 GB RAM, an
  Intel Core2 Duo E8500 CPU and two Parallel-ATA disks in a RAID-1
  configuration} and one smaller with faster disk\footnote{Running
  Debian Wheezy, has 8 GB RAM, an Intel Core i7-3520M CPU and a single
  SSD on SATA-III}.
